Prefetching SPARQL query cacher

### 2016-07-27 dissertation/cache-proxy.tex
qualify HERMES

>>>>

It is further interesting to note the contrast to the HERMES
\cite{adali1996query} system's concept of invariants discussed in
Section~\ref{sec:relcache}: a SPARQL query cache be oblivious
to domain knowledge in a CDN deployment and therefore shouldn't assume any invariants,
except in the possible but unlikely case where the remote server
declares an infinite freshness lifetime for the result of a certain
graph pattern.
